%-------------------------
% Resume in Latex
% Author of the Template : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://quicksilver0.github.io/}{\Large Vladimir Kuzmenkov}} & Email : \href{mailto:vova.kuzmenkov0@gmail.com}{vova.kuzmenkov0@gmail.com}\\
  \href{https://quicksilver0.github.io/}{https://quicksilver0.github.io/} & Mobile : +375-44-5749968 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Applied Data Science with Python Specialization}{coursera.org, University of Michigan}
      {5 course Specialization, Overall Grade Achieved: 99%}{July. 2017 -- Dec. 2017}
    \resumeSubheading
      {Deep Learning Specialization}{coursera.org, deeplearning.ai}
      {5 course Specialization, Overall Grade Achieved: 99.5%}{October. 2017 -- March. 2018}
    \resumeSubheading
      {Data Analyst and Data Scientist Paths}{dataquest.io}
      {Practicing with Data Science projects and technologies}{July. 2017 -- April. 2018}
    \resumeSubheading
      {Belarusian State Medical University}{Minsk, Belarus}
      {General Medicine. Yet, my lifepath led me to IT}{Sept. 2005 -- May. 2010}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Epam Systems}{Minsk, Belarus}
      {System Analyst and Performance Testing}{Aug 2015 - Aug 2016}
      \resumeItemListStart
        \resumeItem{Projects}
          {Streaming platform: online TV, e-commerce - delhaize group}
        \resumeItem{What was I doing?}
          {Essentially the aim was to perform initial analysis of the system, build non-functional "heavy load tests", kick them off, answer the question "how capable the system is", revealing the "bottlenecks", resolve those in cooperation with devs.}
      \resumeItemListEnd
    \resumeSubheading
      {Allied Testing}{Minsk, Belarus; London, UK}
      {Performance Tester}{Jul 2011 - Oct 2014}
      \resumeItemListStart
        \resumeItem{Projects}
          {London Stock Exchange, Deutsche Bank }
        \resumeItem{Testing}
          {Design, build, run load tests, collect and present stats. Essentially answering a question "What is the capacity the system?"
}
        \resumeItem{Workflow}
          {Cooperation with various teams: developers, business analysts, QAs located across different countries.}
        \resumeItem{Impact}
          {System performance I worked with and its' capacity have improved significantly. Subsequently it was all about cost improvement in operations, maintenance, developement for those systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Mercari Price Suggestion Challenge ($100,000 prize Kaggle style data science competition}{Dec 2017 - Jan 2018}
      {Currently top 6\% out of 2.4k participant teams. First place has mrse ~38\%, mine ~42\% on price prediction. https://www.kaggle.com/c/mercari-price-suggestion-challenge}
    \resumeSubItem{US Traffic Fatality Rates}{Feb 2017}
      {Deep Exploration on US Traffic data using BigSql, Machine Learning techniques and presenting most interesting findings in nice visuals via plotly, matplotlib. https://www.kaggle.com/silversurf/us-traffic-getting-to-the-bottom-of-it}
    \resumeSubItem{Text Mining - Hacker News}
      {Topic popularity exploration on Hacker News website since 2007. The results are presented as nice interactive highcharts graph https://quicksilver0.github.io/project/2017/11/29/headlines_popularity.html}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%  \resumeSubItem{Technical}
%    \item{
%      \textbf{Machine Learning:}{Classification, Regression, Data Preprocessing, Visualization, Feature Engineering, Data Scraping}
%      \hfill
%      \textbf{Deep Learning:}{NLP (FastText, RNN, CNN, LSTMs; GloVe; Attention Mechanism), Image Recognition (CNN), Voice Recognition}
%      \hfill
%      \textbf{Explorative Data AnalysisDA}
%      \hfill
%      \textbf{Others}{MySQL, Postgres, BigSQL, git}
%  \resumeSubItem{Coding}
%    \item{
%      \textbf{Data Science:}{Python(Pandas, Numpy, Matplotlib, Seaborn, plotly, scikit-learn, SciPy, Keras, Theano), SQL}
%      \hfill
%      \textbf{Others:}{HTML, CSS, LaTeX, regexps}
%      \hfill
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
